Investigation on GIT

### 2010-04-25 paper.tex
termine la oracion

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
change, since commits are made in the local repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
resource-consuming, and branches are seen by everybody in the 
%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.

>>>>

In a centralized VCS, most of the time commits aren't done until you are sure that 
the change is well written and can be actually shared to everybody else, since the 
commit is going to be shared as soon as it's done. In a DVCS the nature of the commits 
change, since commits are made in the local repository, they tend to be more atomic, 
and commits aren't huge changesets but can be logical, coherent changes.
To do this in a centralized VCS, one would have to create a new branch of the source code, 
and then merge the branch, but creating and merging branches all the time is 
not effortless, and branches are seen by everybody that can access the repository, 
so this is not always done.
%En el sistema distribuido, hay una diferencia conceptual con los sistemas 
%centralizados acerca de la naturaleza de un commit. Se tiende a hacer commits
%más atómicos y lógicos ya que el commit se hace en el repositorio propio, 
%entonces no hay preocupaciones como romper el build.
